\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{top=2.5cm, bottom=2.5cm, left=2cm, right=2cm}
\usepackage{parskip}
\usepackage{microtype}
\usepackage[default]{sourcesanspro}
\usepackage{xcolor}
\usepackage{fancyhdr}
\usepackage[most]{tcolorbox}
\usepackage[hidelinks]{hyperref}
\usepackage{amssymb, amsmath}

\newcommand{\NombreEstudiante}{The real and complex number systems}
\newcommand{\Libro}{Principles of Mathematical Analysis}
\definecolor{StructureColor}{RGB}{40, 80, 120}

\pagestyle{fancy}
\fancyhf{}
\lhead{\color{StructureColor}\textbf{\Libro}}
\rhead{\small\NombreEstudiante}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\headrule}{\hbox to\headwidth{\color{StructureColor}\leaders\hrule height \headrulewidth\hfill}}

\newtcolorbox{exercisebox}[1]{
    enhanced, colback=StructureColor!5!white, colframe=StructureColor,
    coltitle=white, fonttitle=\bfseries\sffamily,
    title={#1}, sharp corners, boxrule=0.5mm
}

\begin{document}
\thispagestyle{fancy}

\begin{exercisebox}{Exercise 1}
    If $r$ is rational ($r \neq 0$) and $x$ is irrational, prove that $r+x$ and $r \cdot x$ are irrational.
\end{exercisebox}

\textbf{Solution}

Let $r=\dfrac{a}{b}$ where $a,b \in \mathbb{Z}$ with $a\neq 0,\quad b\neq 0$ and let $x$ be irrational.

Part 1 - $r+x$ is irrational 

Suppose, for contradiction, that $r+ x$ is rational. Then there exist $c,d\in \mathbb{Z}$ with $d\neq 0$ such that
\[
r + x = \frac{c}{d}.
\]
We can solve for $x$:
\[
x = \frac{c}{d} - r= \frac{c}{d}-\frac{a}{b}=\frac{b\cdot c+a\cdot d}{b\cdot d}
\]
Note that $b\cdot c+a\cdot d, b \cdot d\in \mathbb{Z}$ with $b\cdot d \neq 0$, so $x$ is rational (contradiction).
Therefore $r \cdot x$ is irrational. 

Part 2 - $r\cdot x$ is irrational

Suppose, for contradiction, that $rx$ is rational. Then there exist $c,d\in \mathbb{Z}$ with $d\neq 0$ such that
\[
r \cdot x = \frac{c}{d}.
\]
Since $r\neq 0$, we can solve for $x$:
\[
x = \frac{c}{r\cdot d} = \frac{c\cdot b}{a \cdot d}.
\]
Note that $c\cdot b, a \cdot d\in \mathbb{Z}$ with $a \cdot d \neq 0$, so $x$ is rational (contradiction).
Therefore $r \cdot x$ is irrational. $\blacksquare$

\end{document}